Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
Moved optimized results to appendix

\section{Validity of SUPERCOP results}

@@

\subsection{Theoretical optimized results}
We have not use the fastest available implementations for all of the
candidates, we also know that our bindings creates an overhead for all calls.
Therefore we have tried to calculate the results that could have been achieved
in Tahoe-\ac{LAFS} if we had managed to obtain the speeds of the fastest
implementations in \{SUPERCOP}. The results can be seen in appendix XX.
%TODO: Fik appendix og referanse

%Tables \ref{tbl:tahoe:optimized_g} and \ref{tbl:tahoe:optimized_p} exhibit
%the results calculated using the best \ac{SUPERCOP} implementation for each
%candidate from Section \ref{sec:results:supercop}, the exact sizes for each
%call to the hash function from Section \ref{sec:results:tahoedata}, and
%interpolation to estimate the time to hash a length not recorded by
%\ac{SUPERCOP}. For lengths above 4096B, the numbers for long data lengths are
%used. The results also assume only one core of the reference processor is used.

%\input{tables/tahoe_optimized_p}
%\input{tables/tahoe_optimized_g}

%TODO: Optimaliserte resultater tabell

@@

% Uncomment to enable appendices.
%\appendix
%\appendixpage
%\addappheadtotoc

>>>>

\section{Reliability of \ac{SUPERCOP} results}

@@

\subsection{Theoretical optimized results}
We have not use the fastest available implementations for all of the
candidates, we also know that our bindings creates an overhead for all calls.
Therefore we have tried to calculate the results that could have been achieved
in Tahoe-\ac{LAFS} if we had managed to obtain the speeds of the fastest
implementations in \{SUPERCOP}. The results can be seen in appendix
\ref{appendix:optimzed_sha3}.

@@

% Uncomment to enable appendices.
\appendix
\appendixpage
\addappheadtotoc

\chapter{Optimized SHA-3 candidates in Tahoe-LAFS}
\label{appendix:optimized_sha3}

Tables \ref{tbl:tahoe:optimized_g} and \ref{tbl:tahoe:optimized_p} exhibit
results calculated which theoretically could have been achieved using the best
\ac{SUPERCOP} implementation for each candidate in Tahoe-\ac{LAFS}. The
calculations uses medians from Section \ref{sec:results:supercop} for the speed
of each candidate, the exact sizes for each call to the hash function from
Section \ref{sec:results:tahoedata}, and interpolation to estimate the time to
hash a length not recorded by \ac{SUPERCOP}. For lengths above 4096B, the
numbers for long data lengths are used. The results also assume only one core
of the reference processor (2,833 GHz) is used. We can see that some of the calculations,
e.g. for Shavite3 are worse than the result we achieved in our measurements,
this is probably due to interpollation being an inaccurate method to use for
the shorter lengths of data.

\input{tables/tahoe_optimized_p}
\input{tables/tahoe_optimized_g}
